\documentclass[12pt]{article}

%Packages
\usepackage{multicol}
\usepackage{hyperref}
\bibliographystyle{plainnat}
\usepackage[round]{natbib}

\textwidth=7in
\textheight=9.5in
\topmargin=-1in
\headheight=0in
\headsep=.5in
\hoffset  -.85in

\pagestyle{empty}

\renewcommand{\arraystretch}{2}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
%\footnotemark
%\footnotetext{Footnote text goes here.}

\begin{document}

% Quick Info Header
\begin{center}
{\bf CSCI 3431\ Sec. 1  \ \ MW 4:00 - 5:15 PM,  Lecture:  Loyola 275,  Lab: Loyola 182  
}
\end{center}

\setlength{\unitlength}{1in}

% Horizontal Line
\begin{picture}(6,.1) 
\put(0,0) {\line(1,0){6.25}}         
\end{picture}

% Course Title
\begin{center}
\huge Operating Systems
\end{center}

\vskip.25in
\noindent\textbf{Instructor:} Andrew Valencik,  McNally North 118, andrew@cs.smu.ca

\vskip.25in
\noindent\textbf{Office Hours:} 2:00-3:30PM MW, 1:00-2:00PM TR, and by appointment.

\vskip.25in
\noindent\textbf{Course Website:} \href{http://moodle.cs.smu.ca}{moodle.cs.smu.ca}

\vskip.25in
\noindent\textbf{Textbook:} No textbook purchase will be required. 
Reading material and open source textbooks will be provided when necessary.
With this in mind, the classic textbook and other useful resources are listed at the end.

\vskip.25in
\begin{multicols}{2}
\setlength{\columnseprule}{1pt}
  \noindent\textbf{Calendar Description:} \\
  \noindent\textbf{Course Prerequisites:} \\
  \noindent\textbf{Academic Dishonesty:}  \\
  
  \columnbreak
  \ \\
  Please see 2014-2015 Academic Calendar \\
  \href{http://www.smu.ca/academics/academic-calendar.html}{www.smu.ca/academics/academic-calendar.html}
\end{multicols}

%\vskip.10in
\noindent \textbf{Grading Scheme:} 

\begin{table}[h]
  \centering
  \begin{tabular}{|l|l|l|}
  \hline
  \textbf{Component} & \textbf{Grade} & \textbf{Notes}                  \\ \hline
  Assignments        & 10             & In lab period                   \\ \hline
  Midterm            & 30             & In class                        \\ \hline
  Project            & 20             & Outside class schedule          \\ \hline
  Exam               & 40             & Schedule in regular exam period \\ \hline
  \end{tabular}
\end{table}

%\vspace*{.15in}
\vskip.10in
\noindent\textbf{Late Policy:} Late submissions will not be accepted without prior arrangement.

\vskip.25in
\noindent\textbf{Extra Help}:  Dot not hesitate to come to my office during office hours or by appointment
to discuss a homework problem or any aspect of the course.

\vskip.25in
\noindent\textbf{Attendance}:
Students are expected to attend classes regularly.
Additionally the labs will involve practical applications and work that cannot be replicated via notes.

\vskip.25in
\noindent\textbf{Methods of Course Delivery}:
Class time will consist of traditional lectures supplemented with online videos, demonstrations, and possibly student interaction.
The course moodle will server as the central and trusted repository for all course related materials.

\pagebreak
\noindent \textbf{Learning Outcomes}: 
This course will examine the structure of modern operating systems and their associated components.
There will be an emphasis on applying learned concepts to student written code.

Upon completion of the course, students should understand how operating systems affect applications and projects they may build.
Additionally, students should be able to:

\begin{itemize}
\item Be very comfortable working from a command line interface
\item Understand the OS interrupt mechanism
\item Develop multiple process and multiple threaded applications
\item Build a virtual machine for a specific use
\item Program effectively using system calls
\item Program using inter-process communication
\item Control concurrency and mutual exclusion using semaphores,
\end{itemize}

\vskip.25in
\noindent\textbf{Important Dates}:
\begin{center} \begin{minipage}{5in}
\begin{flushleft}
Withdrawal Deadline \dotfill Month Day\\
Drop Deadline \dotfill Month Day\\
Midterm \dotfill Month Day\\
Final Exam  \dotfill Month Day\\
Project Presentations \dotfill Month Day\\
Project Deadline \dotfill Month Day\\
\end{flushleft}
\end{minipage}
\end{center}

\nocite{*}

\renewcommand{\refname}{List of Additional Resources}
\bibliography{bibliography.csci3431.bib}

\end{document}
